Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-09-28 LaTeX_paper/paper.tex
continue paper

\section{The Objective Of This Paper}
After reading some of the previous literature for this problem, some conclusions could be drawn:
The problem of ``digital'' jigsaw puzzle has been solved many times, and is already well optimized.\newline
On the other hand, the problem of ``real world'' jigsaw puzzle has mostly been ignored
by the academic community.\newline
The first objective for this paper is to fill this void, and been the first formal paper to analyze the
``real world'' jigsaw puzzle problem.\newline
The second objective of this paper is to use the research that has been done to create a labeling tool.\newline
The reason behind this objective is that the biggest challenge for real world puzzles is creating a
reliable comparator~\ref{document:comparator}. That can deal with all the noisy 
mages you get from the real world.\newline
It is easy to see how a machine learning based comparator would probably be the best solution, 
but this has some problems, in fact having to manually scan and label thousands of individual puzzle
pieces to train the model would take ages.
Instead using an automatic tool would be abel to scan a small $4\times4$ puzzle in one shot,
solve it, and return the labeled data in just a couple minutes.

@@

This is the

@@

  \item \textbf{Remove the knobs from he piece}\newline
  To do so the image without holes gets eroded~\ref{fig:s_s_erosion} and then dilated~\ref{fig:s_s_dilatation}.
  This generates an image that resembles the original one, but has no knobs.
  Then the program finds the pixels that are white in the image without holes,
  but not in the image that has been eroded and dilated.
  This generates a set of Blobs~\ref{fig:s_s_no_holes_minus_expansion},
  but again, the shape of the blob is very different depending on what has generated it
  (an “angle” or a “knob”), so they can be classified.
  Then the program removes from the image with no holes all the pixels that are
  close to a Blob generated by a knob, obtaining an image without knobs and holes~\ref{fig:s_s_no_knobs}.

@@

\section{Apling Already Existing Algorithms To The Real World}
Now that the setup is completed, it is possible to test the already existing
algorithms with real world puzzles, to see if they can work. For this test,
the fist algorithm~\ref{document:GCL} has been chosen, because the paper is full of detail.
In particular it had some information about the accuracy of the algorithm in
function to the corruption rate, which are essential for this analysis.
\newline \newline
The tests that have been conducted have shown that our comparator algorithm~\ref{document:my_comparator}
and the “Graph Connection Laplacian” solution~\ref{document:GCL} are not compatible with each other.
A proof for this claim follows.

@@

This section will provide a proof for the incompatibility of
the two algorithms mentioned above.
\newline \newline
The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\ref{document:GCL} takes as input a binary value,
which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.
\subsubsection{Input Data}
To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:

@@

Improving the comparator is probably the best long term solution,
but it comes with a problem:\newline
Manually testing if some pieces fit together, then making a scan, and finally label
them to create a dataset would require hundreds if not thousands of hours.\newline
On the other hand improving the solver is not a good solution long term,
given that it will almost certainly have a worst time complexity,
but could have some major short term benefit \newline
In particular it does not require to create a huge dataset,
and could be used to build one.
In Fact it could solve hundreds of small puzzles,
and automatically label the connections using the solution he created.
\newline\newline
Given the two options, the author of this paper has chosen to focus on improving
the solver algorithm. The choice was driven by the lack of the time needed to build a dataset,
And the belief that creating a new algorithm,
for then using that to build a dataset,
would still be faster compared to building a dataset manually.

>>>>

\section{The Objective Of This Paper}
After reading some of the previous literature for this problem, some conclusions could be drawn:
The problem of ``digital'' jigsaw puzzle has been solved many times, and is already well optimized.\newline
On the other hand, the problem of ``real world'' jigsaw puzzle has mostly been ignored
by the academic community.\newline
The first objective for this paper is to fill this void, and been the first formal paper to analyze the
``real world'' jigsaw puzzle problem.\newline
The second objective of this paper is to use the research that has been done to create a labeling tool.\newline
The reason behind this objective is that the biggest challenge for real world puzzles is creating a
reliable comparator~\ref{document:comparator}. That can deal with all the noisy 
images you get from the real world.\newline
It is easy to see how a machine learning based comparator would probably be the best solution, 
but this has some problems, in fact having to manually scan and label thousands of individual puzzle
pieces to train the model would take ages.
Instead an automatic tool would be abel to scan a small $4\times4$ puzzle in one shot,
solve it, and return the labeled data in just a couple minutes.

@@

To fulfill the objective of this paper three some data to work with are needed.
This section will cover the input data used, and the Splitter~\ref{document:splitter}
and Comparator~\ref{document:comparator} algorithms.

@@

  \item \textbf{Remove the knobs from he piece}\newline
  To do so the image without holes gets eroded~\ref{fig:s_s_erosion} and then dilated~\ref{fig:s_s_dilatation}.
  This generates an image that resembles the original one, but has no knobs.
  Then the program finds the pixels that are white in the image without holes,
  but not in the image that has been eroded and dilated.
  This generates a set of Blobs~\ref{fig:s_s_no_holes_minus_expansion},
  but again, the shape of one blob is very different depending on what has generated it
  (an “angle” or a “knob”), so they can be classified.
  Then the program removes from the image with no holes all the pixels that are
  close to a Blob generated by a knob, obtaining an image without knobs and holes~\ref{fig:s_s_no_knobs}.

@@

\section{Applying Already Existing Algorithms To The Real World}
Now that the setup is completed, it is possible to test the already existing
algorithms with real world puzzles, to see if they can work. For this test,
the fist algorithm~\ref{document:GCL} has been chosen, because the paper is full of detail.
In particular it had some information about the accuracy of the algorithm in
function to the corruption rate, which are essential for this analysis.

The tests that have been conducted have shown that our comparator algorithm~\ref{document:my_comparator}
and the “Graph Connection Laplacian” solution~\ref{document:GCL} are not compatible with each other.
A proof for this claim follows.

@@

This section will provide a proof for the incompatibility of
the two algorithms mentioned above.
\newline
The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\ref{document:GCL} takes as input a binary value,
which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.
\subsubsection{Input Data}
To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:

@@

Improving the comparator is probably the best long term solution,
but it comes with a problem:\newline
Manually testing if some pieces fit together, then making a scan, and finally label
them to create a dataset would require hundreds if not thousands of hours.

On the other hand improving the solver is not a good solution long term,
given that it will almost certainly have a worst time complexity,
but could have some major short term benefit.

In particular it does not require to create a huge dataset,
and could be used to build one.
In Fact it could solve hundreds of small puzzles,
and automatically label the connections using the solution he created.

Given the two options, the author of this paper has chosen to focus on improving
the solver algorithm. The choice was driven by the belief that creating a new algorithm,
for then using that to build a dataset,
would still be faster compared to building a dataset manually.

\section{The Solver}
The Solver that has been created is not the main focus of this paper,
and cannot be considered state-of-the-art if compared with the current best
digital puzzle solver. But can probably be considered so if compared with current
"real world" puzzle Solvers.

\subsection{The Algorithm}
